---
title: "Lab 01 - Hello R!"
author: "Ashton Hunter"
date: "01-31-2022"
output: 
  html_document: 
    fig_height: 7
    highlight: zenburn
---

```{r load-libraries, include=FALSE}
# Load required libraries
library(tidyverse) 
library(datasauRus)
```

# Exercise 1

```{r ex-1}
table(datasaurus_dozen$dataset)
datasaurus_dozen %>%
  count(dataset)
dim(datasaurus_dozen)
names(datasaurus_dozen)
```

According to the help file there are 13 rows and 2 columns. The variables included in data drame are: away, bullseye, circle, dino, h_lines, high_lines, slant_down, slant_up, star, v_lines, wide_lines, x_shape. 


# Exercise 2

```{r ex-2}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}
dino_data %>%
  summarize(r = cor(x, y))
```


# Exercise 3

```{r ex-3}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
```{r}
star_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient for the Dino Data and the Star Data appear to be very similar, they are slightly different. However, not different enough to make a statistical impact in the interpretation. 


# Exercise 4

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
```{r}
circle_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient for the Dino Data and the Circle Data appear to be very similar, they are slightly different. However, not different enough to make a statistical impact in the interpretation. 


# Exercise 5

```{r ex-5}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```


